null_model

### 2020-09-11 analysis/ts_null_model.Rmd
Use weight column

```{r}
library(tidyverse)
library(biodivTS)
library(FD)

@@

Simulation functions
```{r}
get_plot_sample <- function(data, filter_plot, n){
  print(filter_plot)
  plot_data <- data %>% filter(plot_id == filter_plot) %>%
    select(year, id, year_abun)

@@

  get_samp_species <- function(data){
    samp_species <- sample(species_pool, n_distinct(data$id))
    samp_abun <- sample(data$year_abun)

@@

# sample_occurrence <- map(unique(sample_plots$plot_id), get_plot_sample, data = sample_plots, n = n) %>%
#   bind_rows() %>%
#   replace(is.na(.), 0)
# pins::pin(sample_occurrence, board = "github")
sample_occurrence <- pins::pin_get("sample_occurrence", board = "github")

>>>>

```{r}
library(tidyverse)
library(biodivTS)
library(FD)
library(furrr)

@@

Simulation functions
```{r}
get_plot_sample <- function(data, filter_plot, n){
  print(filter_plot)
  plot_data <- data %>% filter(plot_id == filter_plot) %>%
    select(year, id, weight)

@@

  get_samp_species <- function(data){
    samp_species <- sample(species_pool, n_distinct(data$id))
    samp_abun <- sample(data$weight)

@@

sample_occurrence <- future_map(unique(sample_plots$plot_id), get_plot_sample, data = sample_plots, n = n) %>%
  bind_rows() %>%
  replace(is.na(.), 0)
pins::pin(sample_occurrence, board = "github")
sample_occurrence <- pins::pin_get("sample_occurrence", board = "github")
